A Survey of Physical Design Techniques of Information Systems

### 2010-07-09 cs848-db/Paper.tex

@@

\begin{figure}[!t]
\centering
\includegraphics[width=9cm]{figs/Ttree.png}
\caption{T Tree by Lehmen and Carey~\cite{lehman1986study}}
\label{fig:ttree}
\end{figure}

@@

\subsubsection*{Prefetching B+ Trees (pB+ Trees)}

Chen et al.~\cite{chen2001improving} propose using prefetching to improve the performance of B+ Trees. Since current computer systems can prefetch
different data simultaneously, the authors take advantage of this. The idea here is to increase the node size of B+ Trees and employ prefectching at the same
time. In a B+ Tree, every time we move down a level in the tree, a cache miss occurs. Accordingly, prefetching larger size nodes means that we can overlap
multiple cache misses before they occur.

\subsubsection*{$J^{+}-trees$ and $pJ^{+}-trees$}

>>>>

Chen et al.~\cite{chen2001improving} propose using prefetching to improve the performance of B+ Trees. Since current computer systems can prefetch
different data simultaneously, the authors take advantage of this. The idea here is to increase the node size of B+ Trees and employ prefectching at the same
time. In a B+ Tree, every time we move down a level in the tree, a cache miss occurs. Accordingly, prefetching larger sizes nodes means that we can overlap
multiple cache misses before they occur. This is because in one cache mix, extra data is retrieved in parallel with the originally requested data if it can be
predicted sufficiently early. Figure~\ref{fig:prefetching} shows how prefetching retrieves the same data in less time. This method, however, does not
eliminate the full cache miss latency with every level in the tree.

\begin{figure}[!t]
\centering
\includegraphics[width=7cm]{figs/prefetching.png}
\caption{Performance of various B+ Tree searches where a cache miss to memory takes 150 cycles and a subsequent access can begin 10 cycles
later~\cite{chen2001improving}}
\label{fig:prefetching}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=7cm]{figs/Ttree.png}
\caption{T Tree by Lehmen and Carey~\cite{lehman1986study}}
\label{fig:ttree}
\end{figure}

@@

\subsubsection*{J+-trees and pJ+-trees}
\cite{luan2009prefetching}
